\documentclass[aspectratio=169]{beamer}
\usepackage[isSlide]{uiplatex}
\usepackage{lipsum}

\title{template}
\institute{}
\author{}
\date{\empty}

\begin{document}
    \maketitle

    \begin{frame}{OUTLINE}{}
        \tableofcontents
    \end{frame}

    \section{my tools}

    \begin{frame}{myitemize}
        \begin{myitemize}
            \item This 
            \item is
            \item my 
            \item itemize
        \end{myitemize}
    \end{frame}

    \begin{frame}[fragile]{lstpython}
        \begin{marker}
            fragile環境に設定する.
        \end{marker}
        \begin{lstpython}
print("hello, world")
        \end{lstpython}
    \end{frame}

    \section{tcolorbox}

    \begin{frame}{mybox}{}
        \begin{mybox}
            This is mybox.
        \end{mybox}
    \end{frame}

    \begin{frame}{point}{}
        \begin{point}{point}
            This is point.
        \end{point}

        \begin{point}{point and tcblower}
            This is point.
            \tcblower
            This is tcblower.
        \end{point}
    \end{frame}

    \begin{frame}{trititle}{}
        \begin{trititle}{trititle}
            This is trititle.
        \end{trititle}
    \end{frame}

    \begin{frame}{marker}{}
        \begin{marker}
            This is marker.
        \end{marker}
    \end{frame}

    \begin{frame}[fragile]{commandbox}{}
        \begin{marker}
            fragile環境に設定する.
        \end{marker}
        \commandbox*{cd "My Documents"} changes to directory \commandbox{My Documents}. \\
        \commandbox*{dir /A} lists the directory content. \\
        \commandbox*{copy example.txt d:\target} copies \commandbox{example.txt} to
        \commandbox{d:\target}.
    \end{frame}

    \begin{frame}[fragile]{commandshell}{}
\begin{fullcommandshell}
ls -al
cd /usr/lib
\end{fullcommandshell}
\begin{commandshell}
    ls -al
    cd /usr/lib
\end{commandshell}
    \end{frame}

    \section{appendix}

    \begin{frame}[fragile]{fontawesome5}{}
        \faGithub \\
        \faRust \\
        \faPython \\

    \end{frame}

    \section*{bib}

    \begin{frame}[noframenumbering, allowframebreaks]{参考文献}{}
        \mybox{ref.bibに書き込む.}
        \begin{enumerate}
            \item lualatex main.tex
            \item pbibtex main
            \item lualatex main.tex
        \end{enumerate}
        % \scriptsize
        \beamertemplatetextbibitems
        \bibliographystyle{junsrt}
        \bibliography{ref}
    \end{frame}

\end{document}
